---
title: "redcaptools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{redcaptools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(redcaptools)
```

`redcaptools` assists in exporting data from REDCap via the API, converting variable types (e.g. radio-buttons to factors), labelling etc. 

### Exporting from REDCap

REDCap exports generally come in a single files, with repeating elements as new rows, lots of empty variables (e.g. because they don't exist for a given visit). To use the data, it must often be subsetted by form or event, variables selected, etc. 

`redcaptools` eases this by exporting the data by form from the beginning with the `redcap_export_byform` function. 

```{r, eval = FALSE}
token <- "my-redcap-token"
url <- "https://redcap.mydomain.com/api/"

data <- redcap_export_byform(token, url)
```

Other export functions are `redcap_export_meta` (for downloading various metadata objects - currently the data dictionary, form-event-mapping and event tables) and `redcap_export_tbl`, which can be used to use whatever parameters you like for the API (see the REDCap documentation for details). The dataset that REDCap exports through the website interface is accessed for instance via:

```{r, eval = FALSE}
record <- redcap_export_tbl(token, url, "record")
```


### Processing REDCap data

To make the data more usable in R, it's often nice to label data, create factor, convert dates etc. `redcaptools` has functions to help with that too. Each of the following functions also label variables.

The `redcap_prep` function is the easiest to use. It wraps all of the functions in the following section.

```{r, eval = FALSE}
meta <- redcap_export_meta(token, url)
# could also use a data dictionary exported manually

# where all data is in a single dataframe
prepped <- redcap_prep(record, meta$metadata)

# for data split by forms, use sapply
prepped <- sapply(data, redcap_prep, metadata = meta$metadata)
```


#### Create factors

REDCap has both single and multiple choice factor type variables. These need handling separately, so there are two sets of functions.

Lists of the options can be obtained with the `singlechoice_opts` and `multichoice_opts` functions. These are rather for your information.

```{r, eval = FALSE}
singlechoice_opts(meta$metadata)
mutlichoice_opts(meta$metadata)
```

Factors can be created easily with 

```{r, eval = FALSE}
prepped <- sapply(data, singlechoice_factor, metadata = meta$metadata)
prepped <- sapply(prepped, multichoice_factor, metadata = meta$metadata)
```


#### Create `Date`s and `POSIX` variables

As with single and multiple choice variables, `Date` and `POSIX` variables also need handling separately.

```{r, eval = FALSE}
prepped <- sapply(prepped, redcap_prep_dates, metadata = meta$metadata)
prepped <- sapply(prepped, redcap_prep_datetimes, metadata = meta$metadata)
```


